\bf Supplementary Material

### 2025-09-22 manuscript/manuscript.tex
new reply letter

To show that better performance is achieved when using the $K_n(x)$ correction
instead of the $C_n(x)$, we have ad

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions
are very similar and their first two moments are the same. For the purposes of
evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
marginal distribution is from the
Normal family, or
$X_i \sim N(\cdot ; \mu, \sigma^2), \quad i = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_i \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_i \sim \Gamma(\cdot ; \alpha, \beta), \quad i = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
As noted in Subsection~\ref{sub:npbb}, previous literature
suggests varying block size based on the dependence structure of the series.
For this reason,
we also tried implementing our algorithm using the plug-in approach for circular
bootstrap block size introduced in \citet{politis2004automatic}. Results and
a discussion of this additional simulation are provided in a supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating process.

>>>>

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions
are very similar and their first two moments are the same. For the purposes of
evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
marginal distribution is from the
Normal family, or
$X_i \sim N(\cdot ; \mu, \sigma^2), \quad i = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_i \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_i \sim \Gamma(\cdot ; \alpha, \beta), \quad i = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
As noted in Subsection~\ref{sub:npbb}, previous literature
suggests varying block size based on the dependence structure of the series.
For this reason,
we also tried implementing our algorithm using the plug-in approach for circular
bootstrap block size introduced in \citet{politis2004automatic}. Results and
a discussion of this additional simulation are provided in a supplement.
We also compared empirical performance for the block bootstrap KS test when using the $K_n(x)$ correction
versus the $C_n(x)$. The $K_n(x)$ correction was used
in the main manuscript whereas results and a discussion for the
$C_n(x)$ correction is included in the supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating process.

### 2025-09-22 manuscript/supplement.tex
new reply letter

\title{\bf Supplement: Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration}
\if0\blind
{
  \author[1,2]{Mathew Chandy}
  \author[1]{Elizabeth D. Schifano}
  \author[1]{Jun Yan\thanks{
    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}}
  \author[3]{Xianyang Zhang$^{\ast}$ }
  \affil[1]{Department of Statistics, University of Connecticut}
  \affil[2]{Department of Statistics and Data Science, University of California, Los Angeles}
  \affil[3]{Department of Statistics, Texas A\&M University}
  \maketitle
} \fi

@@

@@

>>>>

\title{\bf Supplementary Material}
\if0\blind
{
  \author[1,2]{Mathew Chandy}
  \author[1]{Elizabeth D. Schifano}
  \author[1]{Jun Yan\thanks{
    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}}
  \author[3]{Xianyang Zhang$^{\ast}$ }
  \affil[1]{Department of Statistics, University of Connecticut}
  \affil[2]{Department of Statistics and Data Science, University of California, Los Angeles}
  \affil[3]{Department of Statistics, Texas A\&M University}
  \maketitle
} \fi

@@

\section{Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration}

@@

\section{Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction}

A heuristic justification for the $K_n(x)$ bias correction term was provided in the main manuscript. It may also help to demonstrate
empirically that this the block bootstrap KS test with the $K_n$ bias correction holds its size at least as
well as the block boostrap KS test with the \citet{babu2004goodness} bias correction and is at
least as powerful. For this reason, we conducted a simulation study
with parameter settings identical to the main study in the paper except
for the choice of bias correction.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/normal_C_n}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_n_C_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/gamma_C_n}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_g_C_n}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr_C_n}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the normal family.
  }
  \label{fig:rr_C_n}
\end{figure}

Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term.
